\documentclass[12pt]{article}
\pagestyle{headings}
\setlength{\topskip}{0.5in}
\setlength{\oddsidemargin}{0pt}
\setlength{\evensidemargin}{0pt}
\setlength{\textwidth}{6.5in}
\setlength{\textheight}{8.5in}
%
%
%
\newcommand{\answerbox}{\fbox{\rule{0in}{.3in}\rule{3.5in}{0in}}}
\newcommand{\gradebox}{\fbox{\rule{0in}{.2in}\rule{.2in}{0in}}}
\newcommand{\signbox}{\fbox{\rule{0in}{.2in}\rule{2.5in}{0in}}}
\newcommand{\answera}{\vbox{\vskip 0.45in plus .25in minus .1in}}
\newcommand{\answerA}{\\ \vbox{\vskip 0.35in plus .25in minus .1in}}
\newcommand{\answerB}{\\ \vbox{\vskip 0.50in plus .25in minus .1in}}
\newcommand{\answerC}{\\ \vbox{\vskip 0.75in plus .25in minus .1in}}
\newcommand{\answerD}{\\ \vbox{\vskip 1.00in plus .25in minus .1in}}
\newcommand{\answerE}{\\ \vbox{\vskip 1.25in plus .25in minus .1in}}
\newcommand{\answerF}{\\ \vbox{\vskip 1.50in plus .25in minus .1in}}
\newcommand{\answerG}{\\ \vbox{\vskip 1.75in plus .25in minus .1in}}
\newcommand{\answerH}{\\ \vbox{\vskip 2.00in plus .25in minus .1in}}
\newcommand{\answerI}{\\ \vbox{\vskip 2.50in plus .25in minus .1in}}
%
%
\parindent=0pt
\parskip=12pt plus2pt minus 1pt
%
%
\newlength{\defaultparindent}
\setlength{\defaultparindent}{\parindent}
%
 
\begin{document}
\markright{UNIX Final Exam --- \pageref{page:last} pages}
{\bf Name} (2pts):  \answerbox\ {\bf print}\hfil

Louis Taber --- BUS R5I\\
Introduction to UNIX Operations\\ 
{\bf OPEN BOOK --- OPEN NOTES --- Calculator OK}

If the grade that I have earned in this class is lower than a \gradebox\
please submit a grade of ``Y'' for me.
Signed: \signbox\hfil
%
%
\begin{enumerate}
\item  6pts.  What advantages does UNIX offer over other operating systems?
\answerD
\item  3pts.  Describe the man command.
\answerC
\item  3pts.  Give an example showing the usage of the man command.
\answerA
\item  2pts.  How can you find out who is logged on to the system you are using?
\answerA
\item  2pts.  How can you find out if the user(s) are idle?
\answerA
\item  3pts.  What is a regular expression?
\answerC
\item  6pts.  List 4 UNIX programs that use regular expressions.  
              Give an example using one of the programs.
\answerC
\item  4pts.  What shell regular expression would match 
              the following file names:\\
              bin01.23, bin01.24, bin01.25\\
              but not these:\\
              bin01.22, bin01.26, bin01.27, etc01.25, bin02.23, bin01.256?
\answerA
\item  4pts.  If you wanted to match an asterisk with a regular expression, how
              would you do this?
\answerA
\item  6pts.  Describe the differences between regular expressions and extended
              regular expressions.
\answerB
\item  2pts.  What is meant by the term pipe?
\answerC
\item  3pts.  Give an example using a pipe.
\answerA
\item  3pts.  What is redirection?
\answerC
\item  4pts.  Write a script file that uses redirection 
              to {\bf append} the current path
              and today's date to the file /etc/log.
\answerB
\item  5pts.  What command syntax would be used to create a background process,
              allowing the user to continue working on other tasks?
\answerA
\item  8pts.  What steps are necessary to add a new user to a 
              UNIX system (without using a system management script) ?
\answerD
\item  6pts.  Passwords are the primary security mechanism of 
              most UNIX systems.  What suggestions could users 
              be given for selecting passwords to enhance system security?
\answerC
\item  4pts.  How can the system administrator verify 
              that the users have secure passwords?
\answerC
\item  6pts.  What other security concerns exist on UNIX systems?
\answerC
\item  2pts.   How do you print a file on a UNIX system?
\answerC
\item  4pts.  What do grave accents or back quotes 
              (near the ``one key'' on most keyboards) do in a issued command?
\answerC
\item  4pts.  Give an example that uses grave accents --- ` --- 
              that sets the script variable WORDS to the 
              number of words in the file ``count.this''.
\answerC
\item . 3pts. Send to the ``standard output'' the 
              value in the variable WORDS.
\answerC
\item  4pts.  How do you create the file name.txt with  
              a text editor with only your 
              name in it.  State which editor and describe how you
              exit the editor and save the file to the disk.
\answerC
\item  6pts.  Why is ``C'' important in the UNIX environment? (And what is it?)
\answerC
\item  4pts.  What command could be used to find the 
              occurrences of two adjacent colons ``::'' in 
              the file /etc/passwd.  This could be used to look for users
              without passwords.
\answerC
\item  3pts.  How do you determine the protection of 
              ALL of the files, including hidden files, 
              in your current directory?
\answerA
\item  3pts.  What does the cd command do if it is issued 
              without any arguments.
\answerA
\item  4pts.  Why is it important to log off a 
              system when you are finished using it?
\answerD
\item  3pts.  What UNIX command(s) can be used to display the 
              contents of a file?
              (p.s.  The ``file'' command can be used 
              first to find out if the file is ASCII!)
\answerC
\item  4pts.  Write an sed program to replace all occurrences of ``abc'' 
              in a file with
              ``ABC''.
\answerC
\item  5pts.  Write a shell script that prints out the name of the
              system and the current number of users.
\answerF
\item  3pts.  How do you log on to a UNIX system?
\answerA
\item  4pts.  How do you log off to a UNIX system with stopped jobs?
\answerA
\item  5pts.  What is a shell?  List at least 4 shells.
\answerC
\item  3pts.  What is a shell script?
\answerC
\item  4pts.  What is the recommended first line in a ``csh'' 
              or ``tcsh'' shell script?  Why?
\answerC
\item  5pts.  Describe Internet (with hopefully less than 30 words).
\answerD
\item  3pts.  Describe the use of history when using the C or TCSH shell.
\answerC
\item  3pts.  Describe the use of file name completion 
              when using the C or TCSH shell.
\answerC
\label{page:last}
\end{enumerate}
\end{document}
